Effects of Weather on Maize Yield in Kenya

### 2019-01-16 presentations/January2019/presentation1.tex
presentation

	\begin{itemize}
		\item Total precipitation over rainy seasons
		\item Average temperature during rainy seasons
		\item Average maximum daily temperature during rainy seasons
	\end{itemize}

\item{Less commonly used measures considered:}
	\begin{itemize}
		\item Coefficients of variation: precipitation and temperature
		\item Maximum length of dry spell during rainy seasons
		\item Number of dry spells during rainy seasons
		\item Cumulative degree days over rainy seasons
		\item Number of heatwave days
		\item Cumulative precipitation on days when precip. $>90th$ percentile
	\end{itemize}

@@

@@

\frametitle{ideas}
\color{red}
\begin{itemize}
\item Plot of dependency of precip or some measure and yields..

\end{itemize}
\color{black}
\end{frame}

>>>>

	\begin{itemize}
		\item Total precipitation over rainy seasons
		\item Average temperature during rainy seasons
	\end{itemize}

\item{Less commonly used measures considered:}
	\begin{itemize}
		\item Maximum daily precipitation (floods)
		\item Maximum daily temperature
		\item Coefficients of variation: precipitation and temperature
		\item Maximum length of dry spell during rainy seasons
		\item Number of dry spells during rainy seasons
		\item Number of heatwave days
		\item Cumulative precipitation on days when precip. $>90th$ percentile
	\end{itemize}

@@

\section{Methods}

\begin{frame}
\frametitle{Linear mixed effects models}\label{Methods}

\begin{itemize}
\item Panel: County $\times$ Year
\item Slopes allowed to vary over counties
\end{itemize}

\begingroup
\everymath{\small}

\begin{align*}
\hspace{-0.5cm} \begin{array}{lclll}
 log(y_{\scriptscriptstyle 1t} )&=&\sum_{\scriptscriptstyle m=1}^{\scriptscriptstyle p} \beta^{\scriptscriptstyle m}x^{\scriptscriptstyle m}_{\scriptscriptstyle 1t}+ \sum_{\scriptscriptstyle n=1}^{\scriptscriptstyle q}b^{\scriptscriptstyle n}_{\scriptscriptstyle 1}z^{\scriptscriptstyle n}_{\scriptscriptstyle 1t}+\epsilon_{\scriptscriptstyle 1t} \\[2mm]
 log(y_{\scriptscriptstyle 2t} )&=&\sum_{\scriptscriptstyle m=1}^{\scriptscriptstyle p} \beta^{\scriptscriptstyle m}x^{\scriptscriptstyle m}_{\scriptscriptstyle 2t}+ &\sum_{\scriptscriptstyle n=1}^{\scriptscriptstyle q}b^{\scriptscriptstyle n}_{\scriptscriptstyle 2}z^{\scriptscriptstyle n}_{\scriptscriptstyle 2t}+\epsilon_{\scriptscriptstyle 2t}\\[1mm]
  &\huge{\vdots}\\[-2mm]
  & \huge{\vdots} \\[1mm]
  log(y_{\scriptscriptstyle 47t} )&=&\sum_{\scriptscriptstyle m=1}^{\scriptscriptstyle p} \beta^{\scriptscriptstyle m}x^{\scriptscriptstyle m}_{\scriptscriptstyle 47t}+ &&\sum_{\scriptscriptstyle n=1}^{\scriptscriptstyle q}b^{\scriptscriptstyle n}_{\scriptscriptstyle 47}z^{\scriptscriptstyle n}_{\scriptscriptstyle 47t}+\epsilon_{\scriptscriptstyle 47t}
\end{array}
\end{align*}
\endgroup

$y_{it}$ &$=$& Maize yield t/hectares, county $i$ in year $t$\\
$\boldsymbol{\beta}$ &$=$& Vector of effects of other covariates\\
$X_{i,t}$ &$=$& Matrix of values of other covariates in county $i$ in year $t$\\
$\epsilon_{i,t}$ &$=$& Error term \\
\end{tabular}
\end{small}
\end{table}

\note{Maybe talk about ambigous methodology: the same words used for different terms//a}

\begin{frame}
\frametitle{Linear mixed effects models}\label{Methods}

\begin{itemize}
\item Panel: County $\times$ Year
\item Slopes allowed to vary over counties
\end{itemize}

\begin{columns}

\begin{column}{0.5\textwidth} 
\begingroup
\everymath{\Large}
\begin{align*}
\begin{array}{lcl}
 log(y_{\scriptscriptstyle it} )&=&\sum_{\scriptscriptstyle m=1}^{\scriptscriptstyle p} \beta^{\scriptscriptstyle m}x^{\scriptscriptstyle m}_{\scriptscriptstyle it}+ \sum_{\scriptscriptstyle n=1}^{\scriptscriptstyle q}b^{\scriptscriptstyle n}_{\scriptscriptstyle i}z^{\scriptscriptstyle n}_{\scriptscriptstyle it}+\epsilon_{\scriptscriptstyle it}
\end{array}
\end{align*}
\endgroup
\end{column}

\begin{column}{0.5\textwidth} 
\begingroup
\everymath{\footnotesize}
\begin{align*}
\begin{array}{ll}
i=1,...,47 & \text{counties}
\end{array}
\end{align*}
\endgroup
\end{column}
\end{columns}

$y_{it}$ &$=$& Maize yield t/hectares, county $i$ in year $t$\\
$\alpha_i$ &$=$& Fixed effects), county $i$\\
{\color{darkblue}$\delta$ }&{\color{darkblue}$=$}&{\color{darkblue}{Effect of drought on economy}}\\

$X_{i,t}$ &$=$& Matrix of values of other covariates in county $i$ in year $t$\\
$\epsilon_{i,t}$ &$=$& Error term \\
\end{tabular}
\end{small}
\end{table}

\note{Maybe talk about ambigous methodology: the same words used for different terms//a}

@@

\frametitle{ideas}

\begin{itemize}
\color{red}
\item Plot of dependency of precip or some measure and yields..
\item Maybe also general description of the mixed effects models as I have in the draft
\item Look at the document on google docs 'Yield and climate' to see if I can use something
\end{itemize}
\color{black}
\end{frame}
